---
title: "FMP"
author: "Stavros Dimitriadis"
date: "2024-02-29"
output:
  html_document:
    highlight: default
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
  word_document:
    toc: yes
    toc_depth: '2'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


*Preliminaries*

Let's load needed packages.

```{r libs}
#library(knitr)
library(MSnbase)
library(tidyverse)
library(Biobase)
library(BiocParallel)

library(xcms)
library(faahKO)
library(RColorBrewer)
library(pander)
library(pheatmap)
library(MsExperiment)
library(stats)
library(SummarizedExperiment)
library(mWISE)
library(FELLA)

library(curl)
library(piggyback)
library(CompoundDb)

library(MetaboAnnotation)
```






# STEP 1 :Below we download the database from github to a temporary folder.

```{r, eval = TRUE, echo = TRUE}

#' Download the CompDb database using curl
library(curl)

dbname <- "CompDb.Hsapiens.HMDB.5.0.sqlite"
db_file <- file.path(tempdir(), dbname)
curl_download(
    paste0("https://github.com/jorainer/MetaboAnnotationTutorials/",
           "releases/download/2021-11-02/", dbname),
    destfile = db_file)
```


```{r, eval = FALSE, echo = FALSE}

library(piggyback)

#' Download the SQLite database from github.
dbname <- "CompDb.Hsapiens.HMDB.5.0.sqlite"
pb_download(dbname,
            repo = "jorainer/MetaboAnnotationTutorials",
            tag = "2021-11-02",
            dest = tempdir())
db_file <- file.path(tempdir(), dbname)

```

#STEP 2 : We next load the database using the `CompoundDb` package.



```{r}


library(CompoundDb)
#' Load a CompDb database with compound annotation from HMDB
cdb <- CompDb(db_file)
cdb


```

## Annotation using *m/z* values {#ms1mz}

We next extract all peaks from the `xcms` result object and annotate them using
the `matchMz` function against all compounds from HMDB (the compound annotations
can be extracted from the `CompDb` database with the `compounds` function). The
reference database does not provide *m/z* values but only exact masses for each
compound. Thus, in order to annotate our chromatographic peaks' *m/z* values,
*m/z* values for expected ions of the compounds need to be calculated
first. With `Mass2MzParam` we can configure the parameters for the
annotation. Parameter `adducts` allows to specify the adducts (ions) we expect
to see mostly in the data set. For our example we assume to see mostly `[M+H]+`
and `[M+Na]+` positive ions. With parameters `tolerance` and `ppm` we can
finally define also the absolute and/or *m/z* relative acceptable difference,
respectively, for *m/z* values to be considered matching.



```{r}

library(MetaboAnnotation)

#' Get the chromatographic peaks and add a column with the peak_id
pks <- data.frame(peak_id = rownames(chromPeaks(mov.peaks.mpp)),
                  chromPeaks(mov.peaks.mpp))

#' Set parameters for the m/z-based annotation
param <- Mass2MzParam(adducts = c("[M+H]+", "[M+Na]+"),
                      tolerance = 0, ppm = 10)

#' Perform the matching
pks_match <- matchMz(
    pks,
    compounds(cdb, c("compound_id", "exactmass", "formula", "name")),
    param = param)

pks_match

head(matches(pks_match))

matchedData(pks_match, c("peak_id", "target_name",
                         "target_formula", "adduct"))

matches(pks_match)[, 1] |>
table() |>
mean()


# GET MATCHED COMPOUNDS PER SUBJECT

matches.compound<- matrix(1:260964, nrow=260964, ncol=1)
metabolites.intensity <- matrix(1:260964, nrow=260964, ncol=1)

for (i in 1:260964 ) {
     print(i)
     matched <- matchedData(pks_match[i], c("peak_id", "target_name",
                            "target_formula", "target_compound_id", "adduct")) 
     matches.compound[i,] <- matched[1,4]
}

library(foreach)
library(doParallel)

#setup parallel backend to use many processors
cores=detectCores()
cl <- makeCluster(cores) #not to overload your computer
registerDoParallel(cl)
clusterCall(cl, function(x) .libPaths(x), .libPaths())


#Parallelize for loop

matches.compound <- foreach(i=1:10) %dopar% {
  
  source("C:/Users/mpnsd/Desktop/BARCELONA/MOVIMENT-PROJECT/Metabolomics/matching_metabolites.R") # That is the main point. Source your Function File here.
  temp <- matching_metabolites(i,matchedData) # use your custom function after sourcing 
  temp
   
  # matched <- matchedData(pks_match[i], c("peak_id", "target_name",
  #                          "target_formula", "target_compound_id", "adduct")) 
   #  matches.compound[i,] <- matched[1,4]
}


stopCluster(cl)


#Get the intensity of metabolites
metabolites.intensity <- pks_match@query$into

```




```{r,metabolites.annotation.moviment}

# POSITIVE PRE

#LOAD THE SESSION

load("C:/Users/mpnsd/Desktop/BARCELONA/MOVIMENT-PROJECT/Metabolomics/Dimitriadis_moviment_metabolomics_positive_pre.RData")

#' Get the chromatographic peaks and add a column with the peak_id
pks.pos.pre <- data.frame(peak_id = rownames(chromPeaks(mov.peaks.mpp)),
                  chromPeaks(mov.peaks.mpp))

#' Set parameters for the m/z-based annotation
param <- Mass2MzParam(adducts = c("[M+H]+", "[M+Na]+"),
                      tolerance = 0, ppm = 10)

#' Perform the matching
pks_match.pos.pre <- matchMz(
    pks.pos.pre,
    compounds(cdb, c("compound_id", "exactmass", "formula", "name")),
    param = param)

pks_match.pos.pre

head(matches(pks_match.pos.pre))

matchedData(pks_match.pos.pre, c("peak_id", "target_name",
                         "target_formula", "adduct"))

matches(pks_match.pos.pre)[, 1] |>
table() |>
mean()


# GET MATCHED COMPOUNDS PER SUBJECT

matches.compound.pos.pre <- matrix(1:260964, nrow=260964, ncol=1)
metabolites.intensity.pos.pre <- matrix(1:260964, nrow=260964, ncol=1)

for (i in 1:260964 ) {
     print(i)
     matched <- matchedData(pks_match.pos.pre[i], c("peak_id", "target_name",
                            "target_formula", "target_compound_id", "adduct")) 
     matches.compound.pos.pre[i,] <- matched[1,4]
}


#Get the intensity of metabolites
metabolites.intensity.pos.pre <- pks_match.pos.pre@query$into



#Parallelize for loop

#matches.compound <- foreach(i=1:10, .combine=cbind) %dopar% {
 #   matched <- matchedData(pks_match[i], c("peak_id", "target_name",
 #                           "target_formula", "target_compound_id", "adduct")) 
#     matches.compound <- cbind(matches.compound,matched[1,4])}





# POSITIVE POST

#LOAD THE SESSION

load("C:/Users/mpnsd/Desktop/BARCELONA/MOVIMENT-PROJECT/Metabolomics/Dimitriadis_moviment_metabolomics_positive_post.RData")



#' Get the chromatographic peaks and add a column with the peak_id
pks.pos.post <- data.frame(peak_id = rownames(chromPeaks(mov.peaks.mpp)),
                  chromPeaks(mov.peaks.mpp))

#' Set parameters for the m/z-based annotation
param <- Mass2MzParam(adducts = c("[M+H]+", "[M+Na]+"),
                      tolerance = 0, ppm = 10)

#' Perform the matching
pks_match.pos.post <- matchMz(
    pks.pos.post,
    compounds(cdb, c("compound_id", "exactmass", "formula", "name")),
    param = param)

pks_match.pos.post

head(matches(pks_match.pos.post))

matchedData(pks_match.pos.post, c("peak_id", "target_name",
                         "target_formula", "adduct"))

matches(pks_match.pos.post)[, 1] |>
table() |>
mean()


# GET MATCHED COMPOUNDS PER SUBJECT

matches.compound.pos.post <- matrix(1:260964, nrow=260964, ncol=1)
metabolites.intensity.pos.post <- matrix(1:260964, nrow=260964, ncol=1)

for (i in 1:260964 ) {
     print(i)
     matched <- matchedData(pks_match.pos.post[i], c("peak_id", "target_name",
                            "target_formula", "target_compound_id", "adduct")) 
     matches.compound.pos.post[i,] <- matched[1,4]
}



#Get the intensity of metabolites
metabolites.intensity.pos.post <- pks_match.pos.post@query$into


#########################################################################################


# NEGATIVE PRE

#LOAD THE SESSION

load("C:/Users/mpnsd/Desktop/BARCELONA/MOVIMENT-PROJECT/Metabolomics/Dimitriadis_moviment_metabolomics_negative_pre.RData")

#' Get the chromatographic peaks and add a column with the peak_id
pks.neg.pre <- data.frame(peak_id = rownames(chromPeaks(mov.peaks.mpp)),
                  chromPeaks(mov.peaks.mpp))

#' Set parameters for the m/z-based annotation
param <- Mass2MzParam(adducts = c("[M+H]+", "[M+Na]+"),
                      tolerance = 0, ppm = 10)

#' Perform the matching
pks_match.neg.pre <- matchMz(
    pks.neg.pre,
    compounds(cdb, c("compound_id", "exactmass", "formula", "name")),
    param = param)

pks_match.neg.pre

head(matches(pks_match.neg.pre))

matchedData(pks_match.neg.pre, c("peak_id", "target_name",
                         "target_formula", "adduct"))

matches(pks_match.neg.pre)[, 1] |>
table() |>
mean()


len<-length(pks.neg.pre[,1])

# GET MATCHED COMPOUNDS PER SUBJECT

matches.compound.neg.pre <- matrix(1:len, nrow=len, ncol=1)
metabolites.intensity.neg.pre <- matrix(1:len, nrow=len, ncol=1)

for (i in 1:len ) {
     print(i)
     matched <- matchedData(pks_match.neg.pre[i], c("peak_id", "target_name",
                            "target_formula", "target_compound_id", "adduct")) 
     matches.compound.neg.pre[i,] <- matched[1,4]
}


#Get the intensity of metabolites
metabolites.intensity.neg.pre <- pks_match.neg.pre@query$into











# NEGATIVE POST

#LOAD THE SESSION

load("C:/Users/mpnsd/Desktop/BARCELONA/MOVIMENT-PROJECT/Metabolomics/Dimitriadis_moviment_metabolomics_negative_post.RData")

#' Get the chromatographic peaks and add a column with the peak_id
pks.neg.post <- data.frame(peak_id = rownames(chromPeaks(mov.peaks.mpp)),
                  chromPeaks(mov.peaks.mpp))

#' Set parameters for the m/z-based annotation
param <- Mass2MzParam(adducts = c("[M+H]+", "[M+Na]+"),
                      tolerance = 0, ppm = 10)

#' Perform the matching
pks_match.neg.post <- matchMz(
    pks.neg.post,
    compounds(cdb, c("compound_id", "exactmass", "formula", "name")),
    param = param)

pks_match.neg.post

head(matches(pks_match.neg.post))

matchedData(pks_match.neg.post, c("peak_id", "target_name",
                         "target_formula", "adduct"))

matches(pks_match.neg.post)[, 1] |>
table() |>
mean()


len<-length(pks.neg.post[,1])

# GET MATCHED COMPOUNDS PER SUBJECT

matches.compound.neg.post <- matrix(1:len, nrow=len, ncol=1)
metabolites.intensity.neg.post <- matrix(1:len, nrow=len, ncol=1)

for (i in 1:len ) {
     print(i)
     matched <- matchedData(pks_match.neg.post[i], c("peak_id", "target_name",
                            "target_formula", "target_compound_id", "adduct")) 
     matches.compound.neg.post[i,] <- matched[1,4]
}


#Get the intensity of metabolites
metabolites.intensity.neg.post <- pks_match.neg.post@query$into







```




```{r,find.common.metabolites.group.positive}

#keeping metabolites' intensity
metabolites.intensity.pos.pre

# keeping metabolites' IDs
matches.compound.pos.pre


# keeping the matching of metabolites found in the sample based on m/z with
# libraries
pks.pos.pre


## FIND COMMON METABOLITES ACROSS PRE-INTERVENTION PERIOD IN POSITIVE IONIZATION
## WITH INTERSECTION

idx<-which(pks.pos.pre$sample == 1)
v1<-unique(matches.compound.pos.pre[idx])


idx.pos.pre<-NULL
for (i in 2:82){
    
   idx<-which(pks.pos.pre$sample == i)
   v2<-unique(matches.compound.pos.pre[idx])
   
   
   idx.pos.pre<-intersect(unique(v1),unique(v2))
  
  # new v1 should be the v2    
   v1 <- v2   
  
}


## FIND COMMON METABOLITES ACROSS POST-INTERVENTION PERIOD IN POSITIVE IONIZATION
## WITH INTERSECTION

idx<-which(pks.pos.post$sample == 1)
v1<-unique(matches.compound.pos.post[idx])

idx.pos.post<-NULL
for (i in 2:82){
    
   idx<-which(pks.pos.post$sample == i)
   v2<-unique(matches.compound.pos.post[idx])
   
   
   idx.pos.post<-intersect(unique(v1),unique(v2))
  
  # new v1 should be the v2    
   v1 <- v2   
  
}


## FIND COMMON METABOLITES ACROSS POST-INTERVENTION PERIOD IN POSITIVE IONIZATION
## WITH INTERSECTION

common.metabolites.pos<-intersect(idx.pos.pre,idx.pos.post)
common.metabolites.pos<-common.metabolites.pos[-2] # remove NA


## We got 774 common metabolites across subjects and pre-post intervention period

## Now, we should get the indices 

#which(!lengths(Map(setdiff, list(v2), asplit(common.metabolites.pos, 1))))

#out<-which(apply(common.metabolites.pos, 1, function(x) all(x %in% v2)))

###############################################

##GET THE INDEXES AND THE INTENSITIES OF COMMON METABOLITES BETWEEN
## PRE - POST INTERVENTION ACROSS SUBJECTS


# POSITIVE  - PRE

len<-length(common.metabolites.pos)
int.pos.pre<- matrix(1:len*82, nrow=82, ncol=len)
  

for (i in 1:82){
    idx<-which(pks.pos.pre$sample == i)
    v1<-matches.compound.pos.pre[idx]
    
    index<-NULL
    count<-0
    for (a in 1:length(common.metabolites.pos)) {
         ii <- match(common.metabolites.pos[a],v1)
         
         if (length(ii) > 0) {
            count<-count+1
            index[count]<- ii[1]
         }
        }
    
    #index<-which(v1%in%common.metabolites.pos==TRUE)  
    #out<-intersect(v1,commocommon.metabolites.pos)
    #index<-unique(match(v1,out))
    
    int.pos.pre[i,]<-metabolites.intensity.pos.pre[index]
  }

  
  
# POSITIVE  - POST

len<-length(common.metabolites.pos)
int.pos.post<- matrix(1:len*82, nrow=82, ncol=len)
  

for (i in 1:82){
    idx<-which(pks.pos.post$sample == i)
    v1<-matches.compound.pos.post[idx]
    
    index<-NULL
    count<-0
    for (a in 1:length(common.metabolites.pos)) {
         ii <- match(common.metabolites.pos[a],v1)
         
         if (length(ii) > 0) {
            count<-count+1
            index[count]<- ii[1]
         }
        }
    
    #index<-which(v1%in%common.metabolites.pos==TRUE)  
    #out<-intersect(v1,commocommon.metabolites.pos)
    #index<-unique(match(v1,out))
    
    int.pos.post[i,]<-metabolites.intensity.pos.post[index]
  }


## STATISTICS :

## PRE-INTERVENTION CONDITION GROUP COMPARISONS WITH THE PASSIVE CONTROL

## CONTROL VS PHYSICAL

stat.pos.pre.con.phy<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.pos)){
  
     vec1 <- int.pos.pre[idx.control,a]
     vec2 <- int.pos.pre[idx.physical,a]
     stat <- wilcox.test(vec1,vec2)
     stat.pos.pre.con.phy[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.pos.pre.con.phy<0.05/len)



## CONTROL VS COGNITIVE

stat.pos.pre.con.cog<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.pos)){
  
     vec1 <- int.pos.pre[idx.control,a]
     vec2 <- int.pos.pre[idx.cognitive,a]
     stat <- wilcox.test(vec1,vec2)
     stat.pos.pre.con.cog[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.pos.pre.con.cog<0.05/len)


## CONTROL VS COMBINED

stat.pos.pre.con.comb<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.pos)){
  
     vec1 <- int.pos.pre[idx.control,a]
     vec2 <- int.pos.pre[idx.combined,a]
     stat <- wilcox.test(vec1,vec2)
     stat.pos.pre.con.comb[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.pos.pre.con.comb<0.05/len)


## PRE-POST INTERVENTION COMPARISONS PER GROUP

## CONTROL 

stat.pos.pre.con.con<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.pos)){
  
     vec1 <- int.pos.pre[idx.control,a]
     vec2 <- int.pos.post[idx.control,a]
     # stat <- wilcox.test(vec1,vec2)
     stat <- exactRankTests::wilcox.exact(vec1,vec2)
     stat.pos.pre.con.con[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.pos.pre.con.con<0.05/len)



## PHYSICAL 

stat.pos.pre.phy.phy<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.pos)){
  
     vec1 <- int.pos.pre[idx.physical,a]
     vec2 <- int.pos.post[idx.physical,a]
     #stat <- wilcox.test(vec1,vec2)
     stat <- exactRankTests::wilcox.exact(vec1,vec2)
     stat.pos.pre.phy.phy[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.pos.pre.phy.phy<0.05/len)



## COGNITIVE 

stat.pos.pre.cog.cog<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.pos)){
  
     vec1 <- int.pos.pre[idx.cognitive,a]
     vec2 <- int.pos.post[idx.cognitive,a]
     #stat <- wilcox.test(vec1,vec2)
     stat <- exactRankTests::wilcox.exact(vec1,vec2)
     stat.pos.pre.cog.cog[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.pos.pre.cog.cog<0.05/len)



## COMBINED

stat.pos.pre.comb.comb<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.pos)){
  
     vec1 <- int.pos.pre[idx.combined,a]
     vec2 <- int.pos.post[idx.combined,a]
     #stat <- wilcox.test(vec1,vec2)
     stat <- exactRankTests::wilcox.exact(vec1,vec2)
     stat.pos.pre.comb.comb[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.pos.pre.comb.comb<0.05/len)


```





```{r,find.common.metabolites.group.negative}

#keeping metabolites' intensity
metabolites.intensity.neg.pre

# keeping metabolites' IDs
matches.compound.neg.pre


# keeping the matching of metabolites found in the sample based on m/z with
# libraries
pks.pos.pre


## FIND COMMON METABOLITES ACROSS PRE-INTERVENTION PERIOD IN POSITIVE IONIZATION
## WITH INTERSECTION

idx<-which(pks.neg.pre$sample == 1)
v1<-unique(matches.compound.neg.pre[idx])


idx.neg.pre<-NULL
for (i in 2:82){
    
   idx<-which(pks.neg.pre$sample == i)
   v2<-unique(matches.compound.neg.pre[idx])
   
   
   idx.neg.pre<-intersect(unique(v1),unique(v2))
  
  # new v1 should be the v2    
   v1 <- v2   
  
}


## FIND COMMON METABOLITES ACROSS POST-INTERVENTION PERIOD IN POSITIVE IONIZATION
## WITH INTERSECTION

idx<-which(pks.neg.post$sample == 1)
v1<-unique(matches.compound.neg.post[idx])

idx.neg.post<-NULL
for (i in 2:82){
    
   idx<-which(pks.neg.post$sample == i)
   v2<-unique(matches.compound.neg.post[idx])
   
   
   idx.neg.post<-intersect(unique(v1),unique(v2))
  
  # new v1 should be the v2    
   v1 <- v2   
  
}


## FIND COMMON METABOLITES ACROSS POST-INTERVENTION PERIOD IN POSITIVE IONIZATION
## WITH INTERSECTION

common.metabolites.neg<-intersect(idx.neg.pre,idx.neg.post)
common.metabolites.neg<-common.metabolites.neg[-1] # remove NA


## We got 974 common metabolites across subjects and pre-post intervention period

## Now, we should get the indices 

#which(!lengths(Map(setdiff, list(v2), asplit(common.metabolites.pos, 1))))

#out<-which(apply(common.metabolites.pos, 1, function(x) all(x %in% v2)))

###############################################

##GET THE INDEXES AND THE INTENSITIES OF COMMON METABOLITES BETWEEN
## PRE - POST INTERVENTION ACROSS SUBJECTS


# NEGATIVE  - PRE

len<-length(common.metabolites.neg)
int.neg.pre<- matrix(1:len*82, nrow=82, ncol=len)
  

for (i in 1:82){
    idx<-which(pks.neg.pre$sample == i)
    v1<-matches.compound.neg.pre[idx]
    
    index<-NULL
    count<-0
    for (a in 1:length(common.metabolites.neg)) {
         ii <- match(common.metabolites.neg[a],v1)
         
         if (length(ii) > 0) {
            count<-count+1
            index[count]<- ii[1]
         }
        }
    
    #index<-which(v1%in%common.metabolites.pos==TRUE)  
    #out<-intersect(v1,commocommon.metabolites.pos)
    #index<-unique(match(v1,out))
    
    int.neg.pre[i,]<-metabolites.intensity.neg.pre[index]
  }

  
  
# NEGATIVE  - POST

len<-length(common.metabolites.neg)
int.neg.post<- matrix(1:len*82, nrow=82, ncol=len)
  

for (i in 1:82){
    idx<-which(pks.neg.post$sample == i)
    v1<-matches.compound.neg.post[idx]
    
    index<-NULL
    count<-0
    for (a in 1:length(common.metabolites.neg)) {
         ii <- match(common.metabolites.neg[a],v1)
         
         if (length(ii) > 0) {
            count<-count+1
            index[count]<- ii[1]
         }
        }
    
    #index<-which(v1%in%common.metabolites.pos==TRUE)  
    #out<-intersect(v1,commocommon.metabolites.pos)
    #index<-unique(match(v1,out))
    
    int.neg.post[i,]<-metabolites.intensity.neg.post[index]
  }


## STATISTICS :

## PRE-INTERVENTION CONDITION GROUP COMPARISONS WITH THE PASSIVE CONTROL

## CONTROL VS PHYSICAL

stat.neg.pre.con.phy<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.neg)){
  
     vec1 <- int.neg.pre[idx.control,a]
     vec2 <- int.neg.pre[idx.physical,a]
     stat <- wilcox.test(vec1,vec2)
     stat.neg.pre.con.phy[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.neg.pre.con.phy<0.05/len)



## CONTROL VS COGNITIVE

stat.neg.pre.con.cog<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.neg)){
  
     vec1 <- int.neg.pre[idx.control,a]
     vec2 <- int.neg.pre[idx.cognitive,a]
     stat <- wilcox.test(vec1,vec2)
     stat.neg.pre.con.cog[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.neg.pre.con.cog<0.05/len)


## CONTROL VS COMBINED

stat.neg.pre.con.comb<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.neg)){
  
     vec1 <- int.neg.pre[idx.control,a]
     vec2 <- int.neg.pre[idx.combined,a]
     stat <- wilcox.test(vec1,vec2)
     stat.neg.pre.con.comb[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.neg.pre.con.comb<0.05/len)


## PRE-POST INTERVENTION COMPARISONS PER GROUP

## CONTROL 

stat.neg.pre.con.con<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.neg)){
  
     vec1 <- int.neg.pre[idx.control,a]
     vec2 <- int.neg.post[idx.control,a]
     #stat <- wilcox.test(vec1,vec2)
     stat <- exactRankTests::wilcox.exact(vec1,vec2)
     stat.neg.pre.con.con[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.neg.pre.con.con<0.05/len)



## PHYSICAL 

stat.neg.pre.phy.phy<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.neg)){
  
     vec1 <- int.neg.pre[idx.physical,a]
     vec2 <- int.neg.post[idx.physical,a]
     #stat <- wilcox.test(vec1,vec2)
    stat <- exactRankTests::wilcox.exact(vec1,vec2)
     stat.neg.pre.phy.phy[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.neg.pre.phy.phy<0.05/len)



## COGNITIVE 

stat.neg.pre.cog.cog<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.neg)){
  
     vec1 <- int.neg.pre[idx.cognitive,a]
     vec2 <- int.neg.post[idx.cognitive,a]
     #stat <- wilcox.test(vec1,vec2)
     stat <- exactRankTests::wilcox.exact(vec1,vec2)
     stat.neg.pre.cog.cog[a]<-stat$p.value
  
}

# Bonferroni Correction
which(stat.neg.pre.cog.cog<0.05/len)



## COMBINED

stat.neg.pre.comb.comb<- matrix(1:len, nrow=1, ncol=len)

for (a in 1:length(common.metabolites.neg)){
  
     vec1 <- int.neg.pre[idx.combined,a]
     vec2 <- int.neg.post[idx.combined,a]
     #stat <- wilcox.test(vec1,vec2)
     stat <- exactRankTests::wilcox.exact(vec1,vec2)
     stat.neg.pre.comb.comb[a]<-stat$p.value
    
}

# Bonferroni Correction
which(stat.neg.pre.comb.comb<0.05/len)


```




