---
title: "FMP"
author: "Stavros Dimitriadis"
date: "2024-02-29"
output:
  html_document:
    highlight: default
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
  word_document:
    toc: yes
    toc_depth: '2'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


*Preliminaries*

Let's load needed packages.

```{r libs}
#library(knitr)
library(MSnbase)
library(tidyverse)
library(Biobase)
library(BiocParallel)

library(xcms)
library(faahKO)
library(RColorBrewer)
library(pander)
library(pheatmap)
library(MsExperiment)
library(stats)
library(SummarizedExperiment)
library(mWISE)
library(FELLA)

```



```{r,read.mzml}


rawmsdata.path<-"C:/Users/mpnsd/Desktop/BARCELONA/MOVIMENT-PROJECT/Metabolomics/datasets/HILIC_Positive/moviment_pre"
# mind your working directory!

file <- dir(rawmsdata.path,
            full.name = TRUE,
            pattern = ".mzML")

idx<-c(13,38,46,55,73,1,7:12,14:37,39:45,47:54,56:72,74:82)

file_sorted<-file[idx]


#mem <- readMSData(file, mode = "inMemory")
#mem


#Load data raw MS data using readMSData
dsk<-readMSData(file,mode="onDisk")

class(dsk)
dsk


pd <- data.frame(sample_name = sub(basename(file), pattern = ".mzML",
                                   replacement = "", fixed = TRUE),
                 sample_group  = c(2,3,0,1,2,2,0,0,3,0,0,0,2,1,0,3,1,3,1,1,3,2,2,0,0,1,1,1,2,0,
                                   0,2,0,1,1,0,2,2,0,2,1,1,3,3,0,1,3,1,1,1,0,2,0,3,2,3,0,2,3,2,
                                   1,2,3,1,1,1,3,1,2,0,0,0,0,0,3,1,0,0,2,1,3,2))


mov <- readMsExperiment(spectraFiles = file, sampleData = pd)
mov

```


```{r,first.observations}

spectra(mov)

table(fromFile(mov))


sampleData(mov)


```



```{r,chrom.peaks.all.samples}


## Get the base peak chromatograms. This reads data from the files.
bpis <- chromatogram(mov, aggregationFun = "max")

## Define colors for the two groups
group_colors <- paste0(brewer.pal(4, "Set1")[1:4], "60")
#names(group_colors) <- c("Physical_group", "Cognitive_group","Combined_group","Control_group")

## Plot all chromatograms.
#with group labels
plot(bpis, col = group_colors[sampleData(mov)$sample_group])

# without group labels
plot(bpis)

```


*We next create boxplots representing the distribution of the total ion currents per data file. Such plots can be very useful to spot potentially problematic MS runs. To extract this information, we use the tic() function on the Spectra object within faahko and split the values by file using fromFile().*




```{r, chromaograms.individual}


bpi_1 <- bpis[1, 1]
rtime(bpi_1) |> head()


intensity(bpi_1) |> head()


#test <- filterRt(mov, rt = c(2550, 4250))


## Filter spectra

## creating the BPC on the subsetted data
#bpis <- chromatogram(test, aggregationFun = "max")


## Get the total ion current by file
tc <- spectra(mov) |>
    tic() |>
    split(f = fromFile(mov))
boxplot(tc, col = group_colors[sampleData(mov)$sample_group],
        ylab = "intensity", main = "Total ion current")


```

*In addition, we can also cluster the samples based on similarity of their base peak chromatograms. Samples would thus be grouped based on similarity of their LC runs. For that we need however to bin the data along the retention time axis, since retention times will generally differ between samples. Below we use the bin() function on the BPC to bin intensities into 2 second wide retention time bins. The clustering is then performed using complete linkage hierarchical clustering on the pairwise correlations of the binned base peak chromatograms.*


```{r,hierarcical.clustering}

## Bin the BPC
bpis_bin <- bin(bpis, binSize = 0.25)

## Calculate correlation on the log2 transformed base peak intensities
cormat <- cor(do.call(cbind, lapply(bpis_bin, intensity)))
colnames(cormat) <- rownames(cormat) <- bpis_bin$sample_name

## Define which phenodata columns should be highlighted in the plot
ann <- data.frame(group = bpis_bin$sample_group)
rownames(ann) <- bpis_bin$sample_name

## Perform the cluster analysis
pheatmap(cormat, annotation = ann,
         annotation_color = list(group = group_colors))



```



*Chromatographic peak detection*


```{r,chrom.peak.detection}



# Define the rt and m/z range of the peak area
rtr <- c(350, 380)
mzr <- c(334.9, 335.1)


## extract the chromatogram

chr_raw <- chromatogram(mov, mz = mzr, rt = rtr)

## Make a plot
plot(chr_raw, col = group_colors[chr_raw$sample_group])


# Make a plot for the first 10 samples
mov[1:10,] |>
filterRt(rt = rtr) |>
filterMz(mz = mzr) |>
plot(type = "XIC")


# get chrom peaks - chromPeaks()


cwp <- CentWaveParam()

## Change snthresh parameter
#snthresh(cwp) <- 5
cwp

xchr <- findChromPeaks(chr_raw, param = CentWaveParam(snthresh = 2))

chromPeaks(xchr)

chromPeakData(xchr)


## Define a color for each sample
sample_colors <- group_colors[xchr$sample_group]
## Define the background color for each chromatographic peak
bg <- sample_colors[chromPeaks(xchr)[, "column"]]
## Parameter `col` defines the color of each sample/line, `peakBg` of each
## chromatographic peak.
plot(xchr, col = sample_colors, peakBg = bg)



# Parameters for CentWaveParam:
cwp <- CentWaveParam(peakwidth = c(20, 80), noise = 5000,
                     prefilter = c(6, 5000))

cwp <- CentWaveParam()
snthresh(cwp) <- 2
cwp



#mov.filter <- filterRt(mov, rt = rtr)

mov.peaks <- findChromPeaks(mov, param = cwp)

chromPeaks(mov.peaks) |>
    head()

chromPeakData(mov.peaks)


mpp <- MergeNeighboringPeaksParam(expandRt = 4)
mov.peaks.mpp <- refineChromPeaks(mov.peaks, mpp)

```


*Below we use the data from the chromPeaks() matrix to calculate per-file summaries of the peak detection results, such as the number of peaks per file as well as the distribution of the retention time widths.*

```{r,peak.detection.summary}




summary_fun <- function(z)
    c(peak_count = nrow(z), rt = quantile(z[, "rtmax"] - z[, "rtmin"]))

T <- chromPeaks(mov.peaks.mpp) |>
    split.data.frame(f = chromPeaks(mov.peaks.mpp)[, "sample"]) |>
    lapply(FUN = summary_fun) |>
    do.call(what = rbind)
rownames(T) <- basename(fileNames(mov.peaks.mpp))
pandoc.table(
    T,
    caption = paste0("Summary statistics on identified chromatographic",
                     " peaks. Shown are number of identified peaks per",
                     " sample and widths/duration of chromatographic ",
                     "peaks."))





```

*We can also plot the location of the identified chromatographic peaks in the m/z - retention time space for one file using the plotChromPeaks() function. Below we plot this information for the third sample.*


```{r,plot.chrom.peaks.sample}

plotChromPeaks(mov.peaks.mpp, file = 1)

plotChromPeaks(mov.peaks.mpp, file = 2)

plotChromPeaks(mov.peaks.mpp, file = 3)

plotChromPeaks(mov.peaks.mpp, file = 4)


```




*As a general overview of the peak detection results we can in addition visualize the number of identified chromatographic peaks per file along the retention time axis. Parameter binSize allows to define the width of the bins in rt dimension in which peaks should be counted. This number of chromatographic peaks within each bin is then shown color-coded in the resulting plot.*


```{r,total.chrom.peaks}

plotChromPeakImage(mov.peaks.mpp, binSize = 10)






```


*Finally we plot also the distribution of peak intensity per sample. This allows to investigate whether systematic differences in peak signals between samples are present.*


```{r,peak.intensity.distribution.sample}
#Extract a list of per-sample peak intensities (in log2 scale)

sample_colors <- group_colors[pd$sample_group+1]

ints <- split(log2(chromPeaks(mov.peaks.mpp[1:41])[, "into"]),
              f = chromPeaks(mov.peaks.mpp[1:41])[, "sample"])
boxplot(ints, varwidth = TRUE, col = sample_colors,
        ylab = expression(log[2]~intensity), main = "Peak intensities")
grid(nx = NA, ny = NULL)


ints <- split(log2(chromPeaks(mov.peaks.mpp[42:82])[, "into"]),
              f = chromPeaks(mov.peaks.mpp[42:82])[, "sample"])
boxplot(ints, varwidth = TRUE, col = sample_colors,
        ylab = expression(log[2]~intensity), main = "Peak intensities")
grid(nx = NA, ny = NULL)


```



*Alignment*


```{r, alignment}


# Do the alignment

mov.peaks.mpp.align<- adjustRtime(mov.peaks.mpp, param = ObiwarpParam(binSize = 0.6))


## Extract adjusted retention times
adjustedRtime(mov.peaks.mpp.align) |> head()

## Or simply use the rtime method
rtime(mov.peaks.mpp.align) |> head()

## Get raw (unadjusted) retention times
rtime(mov.peaks.mpp.align, adjusted = FALSE) |> head()




```


*To evaluate the impact of the alignment we plot the BPC on the adjusted data. In addition we plot also the differences between the adjusted and the raw retention times per sample using the plotAdjustedRtime() function. To disable the automatic extraction of all identified chromatographic peaks by the chromatogram() function (which would not make much sense for a BPC) we use chromPeaks = "none" below.*



```{r,alignment.evaluate}


## Get the base peak chromatograms.
bpis_adj <- chromatogram(mov.peaks.mpp.align, aggregationFun = "max", chromPeaks = "none")
par(mfrow = c(3, 1), mar = c(4.5, 4.2, 1, 0.5))

plot(bpis, col = sample_colors)
grid()

plot(bpis_adj, col = sample_colors)
grid()

## Plot also the difference of adjusted to raw retention time.
plotAdjustedRtime(mov.peaks.mpp.align, col = sample_colors)
grid()



```



*Too large differences between adjusted and raw retention times could indicate poorly performing samples or alignment.*

*At last we evaluate also the impact of the alignment on the test peak.*


```{r,adj.retention.times.peak}

par(mfrow = c(2, 1))
## Plot the raw data
plot(chr_raw, col = sample_colors)
grid()
## Extract the chromatogram from the adjusted object
chr_adj <- chromatogram(mov.peaks.mpp.align, rt = rtr, mz = mzr)
plot(chr_adj, col = sample_colors, peakType = "none")
grid()



```




*Correspondence*


```{r, correspondence}


## Perform the correspondence using fixed m/z bin sizes.
pdp <- PeakDensityParam(sampleGroups = sampleData(mov.peaks.mpp.align)$sample_group,
                        minFraction = 0.4, bw = 30)
mov.peaks.mpp.align.corr <- groupChromPeaks(mov.peaks.mpp.align, param = pdp)



#As an alternative we perform the correspondence using m/z relative bin #sizes.

## Drop feature definitions and re-perform the correspondence
## using m/z-relative bin sizes.
mov.peaks.mpp.align.corr.ppm <- groupChromPeaks(
    dropFeatureDefinitions(mov.peaks.mpp.align.corr),
    PeakDensityParam(sampleGroups = sampleData(mov.peaks.mpp.align.corr)$sample_group,
                     minFraction = 0.4, bw = 30))


## Calculate m/z width of features
mzw <- featureDefinitions(mov.peaks.mpp.align.corr)$mzmax - featureDefinitions(mov.peaks.mpp.align.corr)$mzmin
mzw_ppm <- featureDefinitions(mov.peaks.mpp.align.corr.ppm)$mzmax -
                                        featureDefinitions(mov.peaks.mpp.align.corr.ppm)$mzmin

plot(featureDefinitions(mov.peaks.mpp.align.corr.ppm)$mzmed, mzw_ppm,
     xlab = "m/z", ylab = "m/z width", pch = 21,
     col = "#0000ff20", bg = "#0000ff10")

points(featureDefinitions(mov.peaks.mpp.align.corr)$mzmed, mzw, pch = 21,
     col = "#ff000020", bg = "#ff000010")


featureDefinitions(mov.peaks.mpp.align.corr) |> head()


featureValues(mov.peaks.mpp.align.corr, value = "into") |> head()






```



*The performance of peak detection, alignment and correspondence should always be evaluated by inspecting extracted ion chromatograms e.g. of known compounds, internal standards or identified features in general. The featureChromatograms() function allows to extract chromatograms for each feature present in featureDefinitions().* 



```{r,chromatograms}

##
feature_chroms <- featureChromatograms(mov.peaks.mpp.align.corr, features = 1:4)

feature_chroms

#And plot the extracted ion chromatograms. We again use the group color for each identified #peak to fill the area.

plot(feature_chroms, col = sample_colors,
     peakBg = sample_colors[chromPeaks(feature_chroms)[, "sample"]])


#To access the EICs of the second feature we can simply subset the feature_chroms object.

eic_2 <- feature_chroms[2, ]
chromPeaks(eic_2)


```



*Gap Filling*


```{r, gap.filling}


mov.peaks.mpp.align.corr.gap <- fillChromPeaks(mov.peaks.mpp.align.corr, param = ChromPeakAreaParam())

featureValues(mov.peaks.mpp.align.corr.gap, value = "into") |> head()



```



*Save summarized experiment*


```{r,summary.experiment}



res <- quantify(mov.peaks.mpp.align.corr.gap, value = "into", method = "sum")
res

rowData(res)

assayNames(res)

assay(res) |> head()


metadata(res)



```


```{r,QC}


# Set up parameters for RsdFilter
rsd_filter <- RsdFilter(threshold = 0.3,qcIndex = sampleData(mov.peaks.mpp.align.corr.gap)$sample_type == "QC")

# Apply the filter to faakho object
filtered_mov <- filterFeatures(object = mov.peaks.mpp.align.corr.gap, filter = rsd_filter)


# Now apply the same strategy to the res object
rsd_filter <- RsdFilter(threshold = 0.3, qcIndex = res$sample_type == "QC")
filtered_res <- filterFeatures(object = res, filter = rsd_filter, assay = "raw")



```




*mWISE*
*Annotating LC-MS data at once*
*The wrapper function `mWISE.annotation` applies the whole mWISE pipeline at once*

```{r, mWISE}


library(mWISE)

data("KeggDB")
head(KeggDB)


data("Info.Add")
head(Info.Add)

data("sample.keggDB")
Cpd.Add <- CpdaddPreparation(KeggDB = sample.keggDB, do.Par = FALSE)
head(Cpd.Add)


Peak.List.test <- as.data.frame(mov.peaks.mpp.align.corr.gap@featureDefinitions )

x<-Peak.List.test$peakidx

idx<-NULL
for (i in 1:2079) {
  dd<-0
  dd<-x[i]
  idx[i] <- unlist(dd)[1]
}


# Change column names

colnames(Peak.List.test)[1] <- "mz"
colnames(Peak.List.test)[3] <- "mzmax"
colnames(Peak.List.test)[4] <- "rt"
colnames(Peak.List.test)[12] <- "Peak.Id"

#colnames(Peak.List.test)[14]<-"pcgroup"

Peak.List.test[12] <-idx

#Get Intensities values

Int <- featureValues(mov.peaks.mpp.align.corr.gap, value = "into") 


######### SCALING THE INTENSITIES ACROSS SUBJECTS DIMENSIONS

#Int.scaled <- scale(Int, center = TRUE, scale = TRUE)

Int.scaled <- unname(scale(Int, center = TRUE, scale = TRUE))

# Substitute NA with the mean across subjects

for (i in 1:2079){
    xx<-which(is.na(Int[i,]))
    
    if (isEmpty(xx) == FALSE){
       dd<-unname(xx)
       
       sub<-matrix(0, 1, 82)
       sub<-Int[i,]
       
       seqq<-seq(1,82)
       seqq<-seqq[-c(dd)]
       
       sub[dd]<-mean(Int[i,seqq])
       Int[i,]<-sub
       
}
}


# ADD THE INTENSITIES
Peak.List.new<-NULL
Peak.List.new<-Peak.List.test

for (i in 1:82){
    Peak.List.new[,13+i] <- unname(Int[,i])
}

############################PREPROCESSING OF INTENSITIES VALUES
#Estimate the coefficient of variation
# per feature

cv<-NULL

for (i in 1:2079){
    data <-unname(Int[i,])
    idx.not.na <-which(!is.na(data))
    cv[i] <- sd(data[idx.not.na]) / mean(data[idx.not.na]) * 100
}



# GET THE INDEXES OF THE FEATURES WITH A CV HIGHER THAN 30 %
idx.cv <- which(cv > 30)


# GET THE FEATURES WITH AT LEAST ONE NAN ACROSS SUBJECTS/SAMPLES
#na.feat <- which(is.na(Int))


# GET THE INDEX OF FEATURES WITH NO NAN & CV > 30 %
ii<-1:1:2079

ii <- ii[-c(idx.cv)]

idx.feat <- ii

#############################################

#Peak.List.test$npeaks <-mov.peaks.mpp.align.corr.gap@featureDefinitions$npeaks

#Peak.List.test$Peak.Id <-mov.peaks.mpp.align.corr.gap@featureDefinitions$Peak.Id

Intensity.idx <- seq(14,95)

data("sample.graph")
g.metab <- igraph::as.undirected(sample.graph)

## REMOVE FEATURES WITH NAN INPUT & CV <=30

Peak.List.new.feat<-NULL
Peak.List.new.feat <- Peak.List.new

#Peak.List.new.feat <- Peak.List.new[idx.feat,] 


# GIVE A RUN TO THE WHOLE DATASET

Annotated.List <- mWISE.annotation(Peak.List = Peak.List.new.feat,
                                    polarity = "positive",
                                   force.mass.range = TRUE,
                                   mass.range.type = "ppm.mode",
                                   mz.range = NULL, 
                                   ppm =10,
                                   Add.List=NULL,
                                   diffusion.input.type = "probability",
                                   use = "everything",
                                   method = "pearson", 
                                   Freq = 0.5,
                                   Rt.05 = 5,
                                   score = "z",
                                   Cpd.Add = Cpd.Add,
                                   graph = g.metab,
                                   Unique.Annotation = TRUE,
                                   graph.name = "fella",
                                   Intensity.idx = Intensity.idx,
                                   do.Par = FALSE, 
                                   nClust =2)


# RUN THE MWISE PER GROUP BELOW



```




## Evaluating the performance

Finally, the `performanceEvaluation` function can be used to compute 
the performance metrics, using the benchmark data frame `df.Ref`. 
The argument `top.cmps` defines the top K candidates considered 
for the evaluation. 

```{r,mWISE.performance}
performanceEvaluation(Annotated.dataset = Annotated.dataset, 
                      df.Ref = df.Ref, top.cmps = 3)
```






```{r,mwise.control}


idx.control <- which(pd$sample_group == 3)

idxx <- c(13+idx.control)

Intensity.idx <- as.integer(idxx)


#Peak.List.new.feat <- Peak.List.new



Annotated.List.control <- mWISE.annotation(Peak.List =Peak.List.new.feat,
                                   polarity = "positive",
                                   force.mass.range = TRUE,
                                   mass.range.type = "ppm.mode",
                                   mz.range = NULL, 
                                   ppm =10,
                                   Add.List=NULL,
                                   diffusion.input.type = "probability",
                                   use = "everything",
                                   method = "pearson", 
                                   Freq = 0.5,
                                   Rt.05 = 5,
                                   score = "z",
                                   Cpd.Add = Cpd.Add,
                                   graph = g.metab,
                                   Unique.Annotation = TRUE,
                                   graph.name = "fella",
                                   Intensity.idx = Intensity.idx,
                                   do.Par = FALSE, 
                                   nClust =2)





```




```{r,mwise.physical}



idx.physical <- which(pd$sample_group == 0)


idxx <- c(13+idx.physical)

Intensity.idx <- as.integer(idxx)


#Peak.List <- Peak.List.new.feat[ ,13+idx.physical]

Annotated.List.physical<- mWISE.annotation(Peak.List =Peak.List.new.feat,
                                   polarity = "positive",
                                   force.mass.range = TRUE,
                                   mass.range.type = "ppm.mode",
                                   mz.range = NULL, 
                                   ppm =10,
                                   Add.List=NULL,
                                   diffusion.input.type = "probability",
                                   use = "everything",
                                   method = "pearson", 
                                   Freq = 0.5,
                                   Rt.05 = 5,
                                   score = "z",
                                   Cpd.Add = Cpd.Add,
                                   graph = g.metab,
                                   Unique.Annotation = TRUE,
                                   graph.name = "fella",
                                   Intensity.idx = Intensity.idx,
                                   do.Par = FALSE, 
                                   nClust =2)





```



```{r,mwise.cognitive}




idx.cognitive <- which(pd$sample_group == 1)


idxx <- c(13+idx.cognitive)

Intensity.idx <- as.integer(idxx)


#Peak.list <- Peak.List.new.feat[ ,13+idx.cognitive]

Annotated.List.cognitive <- mWISE.annotation(Peak.List =Peak.List.new.feat,
                                   polarity = "positive",
                                   force.mass.range = TRUE,
                                   mass.range.type = "ppm.mode",
                                   mz.range = NULL, 
                                   ppm =10,
                                   Add.List=NULL,
                                   diffusion.input.type = "probability",
                                   use = "everything",
                                   method = "pearson", 
                                   Freq = 0.5,
                                   Rt.05 = 5,
                                   score = "z",
                                   Cpd.Add = Cpd.Add,
                                   graph = g.metab,
                                   Unique.Annotation = TRUE,
                                   graph.name = "fella",
                                   Intensity.idx = Intensity.idx,
                                   do.Par = FALSE, 
                                   nClust =2)



```



```{r,mwise.combined}



idx.combined <- which(pd$sample_group == 2)



idxx <- c(13+idx.combined)

Intensity.idx <- as.integer(idxx)


#Peak.list <- Peak.List.new.feat[ ,13+idx.combined]


Annotated.List.combined <- mWISE.annotation(Peak.List =Peak.List.new.feat,
                                   polarity = "positive",
                                   force.mass.range = TRUE,
                                   mass.range.type = "ppm.mode",
                                   mz.range = NULL, 
                                   ppm =10,
                                   Add.List=NULL,
                                   diffusion.input.type = "probability",
                                   use = "everything",
                                   method = "pearson", 
                                   Rt.05 = 5,
                                   score = "z",
                                   Cpd.Add = Cpd.Add,
                                   graph = g.metab,
                                   Unique.Annotation = TRUE,
                                   Intensity.idx = Intensity.idx,
                                   do.Par = FALSE, 
                                   nClust =2)




```




```{r,FELLA}


library(igraph)
library(magrittr)

library(FELLA)
#library(AnnotationDbi)

library(org.Hs.eg.db)
library(KEGGREST)

library(biomaRt)


### FELLA PREPROCESSING

## ORGANISM STEPS

#STEP 1 : run buildGraphFromKEGGREST()
set.seed(1)
# Filter overview pathways
graph <- buildGraphFromKEGGREST(
    organism = "hsa", 
    filter.path = c("01100", "01200", "01210", "01212", "01230"))


tmpdir <- paste0(tempdir(), "/my_database")


#STEP 2 : run buildDataFromGraph()
buildDataFromGraph(
    keggdata.graph = graph, 
    databaseDir = tmpdir, 
    internalDir = FALSE, 
    matrices = c("hypergeom", "diffusion",
"pagerank"), normality = c("diffusion", "pagerank"),
dampingFactor = 0.85, niter = 100)


#STEP 3 : run loadKEGGdata()
fella.data <- loadKEGGdata(
    databaseDir = tmpdir, 
    internalDir = FALSE, 
    loadMatrix = "none"
)



##### DATA - METABOLITES DERIVED FROM PARTICULAR STUDY


# STEP 1 : GET THE TOP THREE RANKED COMPOUNDS FROM mWISE 
# CONTROL
idx.ranked<-which(Annotated.List.control$Ranked.Tab$Ranking <=3)

input.full <- c(Annotated.List.control$Ranked.Tab$Compound[idx.ranked])  


myAnalysis <- defineCompounds(
    compounds = input.full, 
    data = fella.data)

getInput(myAnalysis)

getExcluded(myAnalysis)



input.fail <- paste0(" ", input.full)
defineCompounds(
    compounds = input.fail, 
    data = fella.data)


# STEP 2 : run enrichment for every available method ()


diff.results<-runDiffusion(
    object = myAnalysis, 
    data = fella.data, 
    approx = "normality", 
    t.df = 10, 
    niter = 1000)


hyp.results<-runHypergeom(
   object = myAnalysis, 
    data = fella.data, 
    p.adjust = "fdr")


pg.results<-runPagerank(
    object = myAnalysis, 
    data = fella.data, 
    approx = "normality", 
    dampingFactor = 0.85, 
    t.df = 10, 
    niter = 1000) 
  
  ############################

myAnalysis <- enrich(
    compounds = input.full, 
    method = listMethods(), 
    approx = "normality", 
    data = fella.data)

show(myAnalysis)



# STEP 3 : show the findings

plot(
    x = myAnalysis, 
    method = "hypergeom", 
    main = "My first enrichment using the hypergeometric test in FELLA", 
    threshold = 1, 
    data = fella.data)


plot(
    x = myAnalysis, 
    method = "diffusion", 
    main = "My first enrichment using the hypergeometric test in FELLA", 
    threshold = 1, 
    data = fella.data)



plot(
    x = myAnalysis, 
    method = "pagerank", 
    main = "My first enrichment using the hypergeometric test in FELLA", 
    threshold = 1, 
    data = fella.data)


# STEP 4 : GENERATE RESULTS IN TABLE AND GRAPH

# For diffusion
myTable <- generateResultsTable(
    object = diff.results, 
    method = "diffusion", 
    threshold = 0.1, 
    data = fella.data)

myTable[myTable$Entry.type == "pathway", ]

myGraph <- generateResultsGraph(
    object = diff.results, 
    method = "diffusion", 
    threshold = 0.1, 
    data = fella.data)

show(myGraph)


myEnzymes<-generateEnzymesTable(
    method = "diffusion", 
    threshold = 0.05, 
    nlimit = 250, 
    LabelLengthAtPlot = 45, 
    capPscores = 1e-6, 
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"),
    object = diff.results, 
    data = fella.data)


go.to.graph<-addGOToGraph(
    graph = myGraph, 
    GOterm = NULL, 
    godata.options = list(
        OrgDb = "org.Hs.eg.db", ont = "CC"),
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"))


# For hypergeom

myTable <- generateResultsTable(
    object = hyp.results, 
    method = "hypergeom", 
    threshold = 0.1, 
    data = fella.data)


# Pathways
myTable[myTable$Entry.type == "CompoundsInPathway", ]


myGraph <- generateResultsGraph(
    object = hyp.results, 
    method = "hypergeom", 
    threshold = 0.1, 
    data = fella.data)

show(myGraph)

# Metabolites
#V(myGraph)$name


myEnzymes<-generateEnzymesTable(
    method = "hypergeom", 
    threshold = 0.05, 
    nlimit = 250, 
    LabelLengthAtPlot = 45, 
    capPscores = 1e-6, 
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"),
    object = hyp.results, 
    data = fella.data)


go.to.graph<-addGOToGraph(
    graph = myGraph, 
    GOterm = NULL, 
    godata.options = list(
        OrgDb = "org.Hs.eg.db", ont = "CC"),
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"))




# For PageRank

myTable <- generateResultsTable(
    object = pg.results, 
    method = "pagerank", 
    threshold = 0.1, 
    data = fella.data)


# Pathways
myTable[myTable$Entry.type == "CompoundsInPathway", ]


myGraph <- generateResultsGraph(
    object = pg.results, 
    method = "pagerank", 
    threshold = 0.1, 
    data = fella.data)

show(myGraph)

# Metabolites
V(myGraph)$name


myEnzymes<-generateEnzymesTable(
    method = "pagerank", 
    threshold = 0.05, 
    nlimit = 250, 
    LabelLengthAtPlot = 45, 
    capPscores = 1e-6, 
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"),
    object = pg.results, 
    data = fella.data)


go.to.graph<-addGOToGraph(
    graph = myGraph, 
    GOterm = NULL, 
    godata.options = list(
        OrgDb = "org.Hs.eg.db", ont = "CC"),
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"))

```




```{r,fella.hc}

##### DATA - METABOLITES DERIVED FROM PARTICULAR STUDY


# STEP 1 : GET THE TOP THREE RANKED COMPOUNDS FROM mWISE 
# CONTROL
idx.ranked<-which(Annotated.List.control$Ranked.Tab$Ranking <=3)

input.full <- c(Annotated.List.control$Ranked.Tab$Compound[idx.ranked])  


hc.myAnalysis <- defineCompounds(
    compounds = input.full, 
    data = fella.data)

getInput(hc.myAnalysis)

getExcluded(hc.myAnalysis)



input.fail <- paste0(" ", input.full)



# STEP 2 : run enrichment for every available method ()


hc.diff.results<-runDiffusion(
    object = hc.myAnalysis, 
    data = fella.data, 
    approx = "normality", 
    t.df = 10, 
    niter = 1000)


hc.hyp.results<-runHypergeom(
   object = hc.myAnalysis, 
    data = fella.data, 
    p.adjust = "fdr")


hc.pg.results<-runPagerank(
    object = hc.myAnalysis, 
    data = fella.data, 
    approx = "normality", 
    dampingFactor = 0.85, 
    t.df = 10, 
    niter = 1000) 
  
  ############################

hc.myAnalysis <- enrich(
    compounds = input.full, 
    method = listMethods(), 
    approx = "normality", 
    data = fella.data)

show(hc.myAnalysis)



# STEP 3 : show the findings

plot(
    x = hc.hyp.results, 
    method = "hypergeom", 
    main = "My first enrichment using the hypergeometric test in FELLA", 
    threshold = 1, 
    data = fella.data)


plot(
    x = hc.diff.results, 
    method = "diffusion", 
    main = "My first enrichment using the diffusion test in FELLA", 
    threshold = 0.1, 
    data = fella.data)



plot(
    x = hc.pg.results, 
    method = "pagerank", 
    main = "My first enrichment using the pagerank test in FELLA", 
    threshold = 0.1, 
    nlimit = 250,
    data = fella.data)


# STEP 4 : GENERATE RESULTS IN TABLE AND GRAPH


# For PageRank

hc.myTable <- generateResultsTable(
    object = hc.pg.results, 
    method = "pagerank", 
    nlimit = 500, 
    threshold = 0.1, 
    data = fella.data)


# Pathways
#hc.myTable[myTable$Entry.type == "CompoundsInPathway", ]


hc.myGraph <- generateResultsGraph(
    object =hc.pg.results, 
    method = "pagerank", 
    nlimit = 500,
    threshold = 0.1, 
    data = fella.data)

#show(hc.myGraph)

# Metabolites
#V(hc.myGraph)$name


hc.myEnzymes<-generateEnzymesTable(
    method = "pagerank", 
    threshold = 0.05, 
    nlimit = 500, 
    LabelLengthAtPlot = 45, 
    capPscores = 1e-6, 
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"),
    object = hc.pg.results, 
    data = fella.data)


hc.go.to.graph<-addGOToGraph(
    graph = hc.myAnalysis, 
    GOterm = NULL, 
    godata.options = list(
        OrgDb = "org.Hs.eg.db", ont = "CC"),
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"))


```





```{r,fella.phy}

##### DATA - METABOLITES DERIVED FROM PARTICULAR STUDY


# STEP 1 : GET THE TOP THREE RANKED COMPOUNDS FROM mWISE 
# CONTROL
idx.ranked<-which(Annotated.List.physical$Ranked.Tab$Ranking <=6)

input.full <- c(Annotated.List.physical$Ranked.Tab$Compound[idx.ranked])  


phy.myAnalysis <- defineCompounds(
    compounds = input.full, 
    data = fella.data)

getInput(phy.myAnalysis)

getExcluded(phy.myAnalysis)



input.fail <- paste0(" ", input.full)




# STEP 2 : run enrichment for every available method ()


phy.diff.results<-runDiffusion(
    object = phy.myAnalysis, 
    data = fella.data, 
    approx = "normality", 
    t.df = 10, 
    niter = 1000)


phy.hyp.results<-runHypergeom(
   object = phy.myAnalysis, 
    data = fella.data, 
    p.adjust = "fdr")


phy.pg.results<-runPagerank(
    object = phy.myAnalysis, 
    data = fella.data, 
    approx = "normality", 
    dampingFactor = 0.85, 
    t.df = 10, 
    niter = 1000) 
  
  ############################

phy.myAnalysis <- enrich(
    compounds = input.full, 
    method = listMethods(), 
    approx = "normality", 
    data = fella.data)

show(phy.myAnalysis)



# STEP 3 : show the findings

plot(
    x = phy.hyp.results, 
    method = "hypergeom", 
    main = "My first enrichment using the hypergeometric test in FELLA", 
    threshold = 1, 
    data = fella.data)


plot(
    x = phy.diff.results, 
    method = "diffusion", 
    main = "My first enrichment using the diffusion test in FELLA", 
    threshold = 0.1, 
    data = fella.data)



plot(
    x = phy.pg.results, 
    method = "pagerank", 
    main = "My first enrichment using the pagerank test in FELLA", 
    threshold = 0.1, 
    data = fella.data)


# STEP 4 : GENERATE RESULTS IN TABLE AND GRAPH


# For PageRank

phy.myTable <- generateResultsTable(
    object = phy.pg.results, 
    method = "pagerank", 
    nlimit = 500,
    threshold = 0.1, 
    data = fella.data)


# Pathways
phy.myTable[myTable$Entry.type == "CompoundsInPathway", ]


phy.myGraph <- generateResultsGraph(
    object = phy.pg.results, 
    method = "pagerank", 
    nlimit = 500,
    threshold = 0.1, 
    data = fella.data)

show(phy.myGraph)

# Metabolites
#V(phy.myGraph)$name


phy.myEnzymes<-generateEnzymesTable(
    method = "pagerank", 
    threshold = 0.05, 
    nlimit = 500, 
    LabelLengthAtPlot = 45, 
    capPscores = 1e-6, 
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"),
    object = phy.pg.results, 
    data = fella.data)


phy.go.to.graph<-addGOToGraph(
    graph = phy.myAnalysis, 
    GOterm = NULL, 
    godata.options = list(
        OrgDb = "org.Hs.eg.db", ont = "CC"),
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"))






```



```{r,fella.cogn}

##### DATA - METABOLITES DERIVED FROM PARTICULAR STUDY


# STEP 1 : GET THE TOP THREE RANKED COMPOUNDS FROM mWISE 
# CONTROL
idx.ranked<-which(Annotated.List.cognitive$Ranked.Tab$Ranking <=6)

input.full <- c(Annotated.List.cognitive$Ranked.Tab$Compound[idx.ranked])  


cog.myAnalysis <- defineCompounds(
    compounds = input.full, 
    data = fella.data)

getInput(cog.myAnalysis)

getExcluded(cog.myAnalysis)



input.fail <- paste0(" ", input.full)




# STEP 2 : run enrichment for every available method ()


cog.diff.results<-runDiffusion(
    object = cog.myAnalysis, 
    data = fella.data, 
    approx = "normality", 
    t.df = 10, 
    niter = 1000)


cog.hyp.results<-runHypergeom(
   object = cog.myAnalysis, 
    data = fella.data, 
    p.adjust = "fdr")


cog.pg.results<-runPagerank(
    object = cog.myAnalysis, 
    data = fella.data, 
    approx = "normality", 
    dampingFactor = 0.85, 
    t.df = 10, 
    niter = 1000) 
  
  ############################

cog.myAnalysis <- enrich(
    compounds = input.full, 
    method = listMethods(), 
    approx = "normality", 
    data = fella.data)

show(cog.myAnalysis)



# STEP 3 : show the findings

plot(
    x = cog.hyp.results, 
    method = "hypergeom", 
    main = "My first enrichment using the hypergeometric test in FELLA", 
    threshold = 1, 
    data = fella.data)


plot(
    x = cog.diff.results, 
    method = "diffusion", 
    main = "My first enrichment using the diffusion test in FELLA", 
    threshold = 0.1, 
    data = fella.data)



plot(
    x = cog.pg.results, 
    method = "pagerank", 
    main = "My first enrichment using the pagerank test in FELLA", 
    threshold = 0.1, 
    data = fella.data)


# STEP 4 : GENERATE RESULTS IN TABLE AND GRAPH


# For PageRank

cog.myTable <- generateResultsTable(
    object = cog.pg.results, 
    method = "pagerank", 
    nlimit = 500,
    threshold = 0.1, 
    data = fella.data)


# Pathways
cog.myTable[myTable$Entry.type == "CompoundsInPathway", ]


cog.myGraph <- generateResultsGraph(
    object = cog.pg.results, 
    method = "pagerank", 
    threshold = 0.1, 
    data = fella.data)

show(cog.myGraph)

# Metabolites
#V(cog.myGraph)$name


cog.myEnzymes<-generateEnzymesTable(
    method = "pagerank", 
    threshold = 0.05, 
    nlimit = 250, 
    LabelLengthAtPlot = 45, 
    capPscores = 1e-6, 
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"),
    object = cog.pg.results, 
    data = fella.data)


cog.go.to.graph<-addGOToGraph(
    graph = cog.myAnalysis, 
    GOterm = NULL, 
    godata.options = list(
        OrgDb = "org.Hs.eg.db", ont = "CC"),
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"))







```




```{r,fella.comb}


##### DATA - METABOLITES DERIVED FROM PARTICULAR STUDY


# STEP 1 : GET THE TOP THREE RANKED COMPOUNDS FROM mWISE 
# CONTROL
idx.ranked<-which(Annotated.List.combined$Ranked.Tab$Ranking <=6)

input.full <- c(Annotated.List.combined$Ranked.Tab$Compound[idx.ranked])  


comb.myAnalysis <- defineCompounds(
    compounds = input.full, 
    data = fella.data)

getInput(comb.myAnalysis)

getExcluded(comb.myAnalysis)



input.fail <- paste0(" ", input.full)




# STEP 2 : run enrichment for every available method ()


comb.diff.results<-runDiffusion(
    object = comb.myAnalysis, 
    data = fella.data, 
    approx = "normality", 
    t.df = 10, 
    niter = 1000)


comb.hyp.results<-runHypergeom(
   object = comb.myAnalysis, 
    data = fella.data, 
    p.adjust = "fdr")


comb.pg.results<-runPagerank(
    object = comb.myAnalysis, 
    data = fella.data, 
    approx = "normality", 
    dampingFactor = 0.85, 
    t.df = 10, 
    niter = 1000) 
  
  ############################

comb.myAnalysis <- enrich(
    compounds = input.full, 
    method = listMethods(), 
    approx = "normality", 
    data = fella.data)

show(comb.myAnalysis)



# STEP 3 : show the findings

plot(
    x = comb.hyp.results, 
    method = "hypergeom", 
    main = "My first enrichment using the hypergeometric test in FELLA", 
    threshold = 1, 
    data = fella.data)


plot(
    x = comb.diff.results, 
    method = "diffusion", 
    main = "My first enrichment using the diffusion test in FELLA", 
    threshold = 0.1, 
    data = fella.data)



plot(
    x = comb.pg.results, 
    method = "pagerank", 
    main = "My first enrichment using the pagerank test in FELLA", 
    threshold = 0.1, 
    data = fella.data)


# STEP 4 : GENERATE RESULTS IN TABLE AND GRAPH


# For PageRank

comb.myTable <- generateResultsTable(
    object = comb.pg.results, 
    method = "pagerank", 
    nlimit = 500,
    threshold = 0.1, 
    data = fella.data)


# Pathways
comb.myTable[myTable$Entry.type == "CompoundsInPathway", ]


comb.myGraph <- generateResultsGraph(
    object = comb.pg.results, 
    method = "pagerank", 
    nlimit = 500,
    threshold = 0.1, 
    data = fella.data)

show(comb.myGraph)

# Metabolites
comb.myGraph$name


comb.myEnzymes<-generateEnzymesTable(
    method = "pagerank", 
    threshold = 0.05, 
    nlimit = 500, 
    LabelLengthAtPlot = 45, 
    capPscores = 1e-6, 
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"),
    object = comb.pg.results, 
    data = fella.data)


comb.go.to.graph<-addGOToGraph(
    graph = comb.myAnalysis, 
    GOterm = NULL, 
    godata.options = list(
        OrgDb = "org.Hs.eg.db", ont = "CC"),
    mart.options = list(
        biomart = "ensembl", dataset = "hsapiens_gene_ensembl"))





```



```{r,common.outcome.groups}

#HC vs GROUPS
all_equal(hc.myTable,phy.myTable)


all_equal(hc.myTable,cog.myTable)

all_equal(hc.myTable,comb.myTable)


# between groups
all_equal(phy.myTable,cog.myTable)

all_equal(phy.myTable,comb.myTable)

all_equal(cog.myTable,comb.myTable)






hc.myTable.diff <- generateResultsTable(
    object = hc.diff.results, 
    method = "diffusion", 
    threshold = 0.1, 
    data = fella.data)

phy.myTable.diff <- generateResultsTable(
    object = phy.diff.results, 
    method = "diffusion", 
    threshold = 0.1, 
    data = fella.data)

cog.myTable.diff <- generateResultsTable(
    object = cog.diff.results, 
    method = "diffusion", 
    threshold = 0.1, 
    data = fella.data)

comb.myTable.diff <- generateResultsTable(
    object = comb.diff.results, 
    method = "diffusion", 
    threshold = 0.1, 
    data = fella.data)



all_equal(hc.myTable.diff,phy.myTable.diff)

all_equal(hc.myTable.diff,cog.myTable.diff)

all_equal(hc.myTable.diff,comb.myTable.diff)


# between groups
all_equal(phy.myTable.diff,cog.myTable.diff)

all_equal(phy.myTable.diff,comb.myTable.diff)

all_equal(cog.myTable.diff,comb.myTable.diff)

```







